Proposal: DINO Methods for Style Transfer

### 2022-03-04 Proposal.tex
Method Subsections
method 1 proposal

>>>>

We have four different idea for brining the success of the DINO method to the domain of style transfer.

\subsection{DINO Content Encoder}

We replace the content encoder with a transformer trained by DINO and then train the style and decoders using the regular style transfer paradigm. The idea being that the DINO models robust features vectors may act as powerful abstractions of the information that can be decoded with the new style.

\subsection{Pre-trained DINO Content Encoder}

\subsection{DINO Training for Encoders}

\subsection{Modified DINO Training for Encoders}
